\begin{frame}{Reference}

\begin{thebibliography}{}

\bibitem[Bae and Park, 2000]{arc_BP}
Bae, Y. and Park, C.~Y. (2000).
\newblock An upper bound of arc index of links.
\newblock {\em Mathematical Proccedings of the Cambridge Philosophical
  Society}, 129(3):491--500.

\bibitem[Cromwell, 1995]{openbook1_Cromwell}
Cromwell, P.~R. (1995).
\newblock Embedding knots and links in an open book {I}:{B}asic properties.
\newblock {\em Topology and its Applications}, 64:37--58.

\bibitem[Cromwell, 1998]{arc_Cromwell}
Cromwell, P.~R. (1998).
\newblock Arc presentation of knots and links.
\newblock {\em BANACH CENTER PUBLICATIONS}, 42:57--64.

\bibitem[Cromwell and Nutt, 1996]{openbook2_Cromwell}
Cromwell, P.~R. and Nutt, I.~J. (1996).
\newblock Embedding knots and links in an open book {II}:{B}ounds on arc index.
\newblock {\em Mathematical Proceedings of the Cambridge Philosophical
  Society}, 119(2):309--319.

\bibitem[Dabrowski-Tumanski et~al., 2024]{theta_protein}
Dabrowski-Tumanski, P., Goundaroulis, D., Stasiak, A., and Sulkowska, J.~I.
  (2024).
\newblock $\theta$-curves in proteins.
\newblock {\em Protein Science}, 33(9).
\end{thebibliography}
\end{frame}

\begin{frame}
\begin{thebibliography}
  \bibitem[Jang et~al., 2016]{brunnian_theta}
  Jang, B., Kronaeur, A., Luitel, P., Medici, D., Taylor, S.~A., and Zupan, A.
    (2016).
  \newblock New examples of brunnian theta graphs.
  \newblock {\em Involve a Journal of Mathematics}, 9(5).
  
  \bibitem[Lee and Jin, 2014]{arc_pretzel}
  Lee, H.~J. and Jin, G.~T. (2014).
  \newblock Arc index of pretzel knots of type $(-p,q,r)$.
  \newblock {\em Proceedings of the American Mathematical Society Series B},
    1:135--147.
  
  \bibitem[Lee et~al., 2024]{arc_1313}
  Lee, H.~J., Lee, Y., Lee, C., Park, Y., Kim, H., and Jin, G.~T. (2024).
  \newblock Minimal grid diagrams of the prime knots with crossing number 13 and
    arc index 13.
  
  \bibitem[Lee et~al., 2019]{arc_spacial}
  Lee, M.~J., No, S., and Oh, S. (2019).
  \newblock Arc index of spatial graphs.
  \newblock {\em Journal of Graph Theory}, 90(3).
  
  \bibitem[Moriuchi, 2007]{theta_7}
  Moriuchi, H. (2007).
  \newblock An enumeration of theta-curves with up to seven crossings.
  \newblock {\em Journal of Knot Theory and Its Ramifications}, 18(2):167--197.
  
  \bibitem[Morton and Beltrami, 1998]{arc_kauffman}
  Morton, H.~R. and Beltrami, E. (1998).
  \newblock Arc index and the kauffman polynomial.
  \newblock {\em Mathematical Proceedings of the Cambridge Philosophical
    Society}, 123(1):41--48.
  
  \bibitem[Wolcott, 1986]{kinoshita}
  Wolcott, K. (1986).
  \newblock {\em Geometry and topology: manifolds, varieties, and knots}, chapter
    The Knotting of Theta Curves and Other Graphs in $S^3$, pages 325--346.
  \newblock CRC Press.
  
  \bibitem[Yamada, 1989]{yamada}
  Yamada, S. (1989).
  \newblock An invariant of spatial graphs.
  \newblock {\em J. Graph Theory}, 13(5):537--551.  
\end{thebibliography}
\end{frame}
